Learning Auditory Similarities Between Instrumental Playing Techniques

### 2020-06-05 paper/paper.tex
caption for violin figure

\vspace{1cm}

@@

\caption{\csentence{Violin scattering}}
\label{fig:violin-scattering}
\end{figure}

>>>>

\csentence{(a)}\hspace{0.28\textwidth}
\csentence{(b)}\hspace{0.28\textwidth}
\csentence{(c)}
\vspace{1cm}

@@

\csentence{(d)}\hspace{0.28\textwidth}
\csentence{(e)}\hspace{0.28\textwidth}
\csentence{(f)}

\caption{\csentence{Six playing techniques of the violin.}
Subfigures:
(a) ordinario, (b) sul tasto, (c) tremolo, (d) staccato, (e) nonvibrato, and (f) sforzando.
In each subfigure, the top image shows the wavelet scalogram, as a function of time $t$ (in seconds) and frequency $\lambda$ (in Hertz).
Conversely, the bottom image shows the average time--frequency scattering coefficients, as a function of temporal modulation rate $\alpha$ (in Hertz) and frequential modulation scale $\beta$ (in cycles per octave).
Darker shades denote greater values of acoustic energy.
Note that the ordinary technique (a) contains vibrato.}
\label{fig:violin-scattering}
\end{figure}
